\documentclass[letterpaper,11pt]{article}

\input{styling.sty}

\newif\ifwebdev
\newif\ifmobile
\newif\ifswift

\ifdefined\showmobile
  \mobiletrue
\fi

\ifdefined\showweb
  \webdevtrue
\fi

\ifdefined\showswift
  \swifttrue
  \mobiletrue
\fi

%-------------------------------------------
%%%%%% RESUME %%%%%%

\begin{document}

%------------HEADING------------

\begin{center}
    \textbf{\Huge \scshape Erik Gustavo Bautista Santibañez}\\
    \vspace{1px}
    Irvine, CA $|$ 
    \href{mailto:contact@erikb.dev}{\underline{contact@erikb.dev}} $|$ 
    \href{https://erikb.dev}{\underline{Website}} $|$
    \href{https://linkedin.com/in/erikbautista}{\underline{LinkedIn}} $|$
    \href{https://github.com/erikbdev}{\underline{GitHub}}
\end{center}

%--------SUMMARY--------%
% \ifsummary
%   \section{Summary}
%   \begin{itemize}[leftmargin=0.15in, label={}]
%     \item{Creative iOS Developer with four years of experience in Swift and SwiftUI.}
%   \end{itemize}
% \fi

%--------TECHNICAL SKILLS--------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Swift, TypeScript, JavaScript, HTML, Rust, Python} \\
      \textbf{Frameworks}{:
        \ifmobile{SwiftUI, UIKit, AppKit, Concurrency, Core Data, Observation, AVKit, Vapor, Hummingbird}\fi
        \ifwebdev{\ifmobile{, }\fi Node.js, Vue.js, Vite, Next.js, Express, React, MariaDB}\fi
      } \\
      \textbf{Tools}{: VSCode, \ifmobile{Xcode, }\fi Git, GitHub Actions (CI/CD), YouTrack, AWS (EC2), Hetzner (Cloud), Cloudflare, Docker} \\
    }}
  \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Product Manager}{Feb. 2024 - Dec. 2024}
      {Irvinesoft Inc}{Irvine, California}
      \resumeItemListStart
        \resumeItem{Collaborated with cross-functional teams to ensure seamless integration of features while also maintaining stability across releases.}
        \ifmobile
          \resumeItem{Optimized application rendering, resulting in 50\% performance improvement across \ifmobile{iOS and macOS }\fi platforms.}
          \resumeItem{Redesigned key components and maintained \href{https://apps.apple.com/us/app/bookpod-audiobooks-podcasts/id6473756889}{\underline{BookPod}}, improving user experience and following best practices from Apple's Human Interface Guidelines.}
          \resumeItem{Designed and implemented \href{https://apps.apple.com/us/app/ai-voice-studio/id6484401690}{\underline{AI Voice Studio}} using SwiftUI, enabling rapid prototyping and deployments.}
        \fi
        \ifwebdev
          \resumeItem{Designed and developed \href{https://apps.shopify.com/image-cropper-and-uploader}{\underline{Croppy}}, a Shopify Theme App Extension built using Vue.js, Vite, and Express.}
            \resumeItemListStart
              \resumeItem{Provides tools for customers to crop and upload images to orders, enhancing Shopify theme functionality.}
              \resumeItem{Designed a scalable backend with Express.js to handle image uploads, storage, and retrieval, using a cloud database for persistent storage.}
              \resumeItem{Implemented subscription model based on the number of images uploaded by customers, utilizing Shopify’s subscription API to manage billing and pricing tiers.}
            \resumeItemListEnd
        \fi
      \resumeItemListEnd

    \resumeSubheading
      {Test Automation Internship}{Jun. 2020 - Aug. 2020}
      {Accenture}{Austin, Texas}
      \resumeItemListStart
        \resumeItem{Developed unit tests for various scenarios, increasing the quality assurance for the product.}
        \resumeItem{Collaborated with cross-functional teams to report issues found white testing.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Technical Support Specialist}{Mar. 2020 - Jun. 2020}
    %   {OneSupport}{Austin, Texas}
    %   \resumeItemListStart
    %     \resumeItem{}
    %   \resumeItemListEnd

    \resumeSubheading
      {Information Technology Internship}{Jun. 2019 - Aug. 2019}
      {KIPP Texas Public Schools}{Austin, Texas}
      \resumeItemListStart
        \resumeItem{Serviced over 100+ laptops within the first week of employment.}
        \resumeItem{Performed diagnostics, repairs, and utilized problem-solving skills to identify and resolve technical issues.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%------------PROJECTS------------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\href{https://erikb.dev/showcase/mochi}{\underline{\textbf{Mochi}}} $|$ \emph{Content Viewer for Apple Devices}}{Aug. 2023 -- Feb. 2024}
        \resumeItemListStart
          \ifmobile
            \resumeItem{Designed and developed iOS and macOS application using Swift 5.9, SwiftUI, and The Composable Architecture.}
            \resumeItem{Implemented modular-based source system, allowing users to extend the functionality of the application.}
            \resumeItem{Facilitated releases on TestFlight and utilized GitHub for issues reporting.}
          \else
            \ifwebdev
            \else
              % Add a stub to not cause issues
              \item {}
            \fi
          \fi
          \ifwebdev
            \resumeItem{Developed using Next.js, MDX, TypeScript, and Tailwind CSS.}
            \resumeItem{Built a custom documentation page to help users easily navigate and understand how to use the app.}
            \resumeItem{Focused on creating an intuitive user interface while ensuring a seamless browsing experience.}
          \else
            \ifmobile
            \else
              % Add a stub to not cause issues
              \item {}
            \fi
          \fi
        \resumeItemListEnd

      \ifmobile
        \resumeProjectHeading
          {\textbf{Anime Now!} $|$ \emph{SwiftUI, Swift}}{Sep. 2022 -- Mar. 2023}
          \resumeItemListStart
            \resumeItem{Designed and developed using SwiftUI and The Composable Architecture, reaching over 500 stars on GitHub.}
            \resumeItem{Added the ability to track progress and create watchlists via Core Data.}
            \resumeItem{Delivered new features based on community feedback.}
            \resumeItem{Utilized GitHub Actions to provide continuous integration and deployment.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\href{https://github.com/safer-together-project/app}{\underline{\textbf{Safer Together}}} $|$ \emph{UIKit, Core Data, Python}}{Sep. 2021 -- Mar. 2022}
          \resumeItemListStart
            \resumeItem{Developed an iOS application using UIKit, and FastAPI serving as the web server.}
            \resumeItem{Implemented a report system for notifying any potential exposures, communicating between the server and client.}
            \resumeItem{Manage server and local database synchronization for a more consistent data flow.}
          \resumeItemListEnd
      \fi

      \ifwebdev
        \resumeProjectHeading
          {\href{https://erikb.dev/showcase/jmephotovideo}{\underline{\textbf{Juan Escobedo Photography}}} $|$ \emph{Photo and Video Portfolio}}{Aug. 2021 -- Oct. 2021}
          \resumeItemListStart
            \resumeItem{Developed using Next.js, Bootstrap, and TypeScript to enhance performance and maintainability.}
            \resumeItem{Integrated event galleries from SmugMug API to enable clients to view their content, increasing user interaction.}
            \resumeItem{Gained hands-on experience with modern frontend development practices and API integration.}
        \resumeItemListEnd

        \resumeProjectHeading
          {\href{https://erikb.dev/showcase/wego}{\underline{\textbf{We-Go}}} $|$ \emph{Autonomous Vehicle Scheduling Platform}}{Jan. 2021 -- Apr. 2021}
          \resumeItemListStart
            \resumeItem{Collaborated in a cross-functional team, serving as Scrum Master, DevOps Engineer, and Full-Stack Developer.}
            \resumeItem{Applied Agile methodologies to ensure iterative development and continuous improvement.}
            \resumeItem{Developed using HTML, Bootstrap, and jQuery for a responsive user interface.}
            \resumeItem{Implemented a robust backend using Python, FastAPI, and MongoDB to support real-time scheduling and data management.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\href{https://erikb.dev/showcase/grimewear}{\underline{\textbf{Grimewear}}} $|$ \emph{Ecommerce Website}}{Aug. 2020 -- Nov. 2020}
          \resumeItemListStart
            \resumeItem{Developed a retro Windows 95-inspired e-commerce site using JavaScript, HTML, CSS, JavaScript, and jQuery.}
            \resumeItem{Integrated Shopify API to enable seamless online shopping experience.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\href{https://erikb.dev/showcase/outsidelookingin}{\underline{\textbf{OUTSIDELOOKINGIN}}} $|$ \emph{Lifestyle Website}}{Apr. 2020 -- Jul. 2020}
          \resumeItemListStart
            \resumeItem{Built a retro-themed website using HTML, CSS, JavaScript, and jQuery.}
            \resumeItem{Gained hands-on experience with DOM manipulation, allowing interactive and dynamic updates.}
          \resumeItemListEnd
      \fi

      \ifmobile
        \resumeProjectHeading
          {\href{https://github.com/erikbdev/PrismUI}{\underline{\textbf{PrismUI}}} $|$ \emph{AppKit, SwiftUI, Objective-C, C++}}{Sep. 2019 -- Jun. 2022}
          \resumeItemListStart
            \resumeItem{Designed and developed macOS application that interacts with HID USB to modify keyboard lighting.}
            \resumeItem{Utilized Apple's native libraries to establish intercommunication between hardware and software.}
            \resumeItem{Transitioned from Objective-C to Swift and SwiftUI, reducing error-prone code and increase maintainability.} 
          \resumeItemListEnd

        % \resumeProjectHeading
        %   {\textbf{ESPLightController} $|$ \emph{Andriod, Java, Jetpack}}{Mar. 2019 -- Sep. 2019}
        %   \resumeItemListStart
        %     \resumeItem{Communicates with embedded controllers via local Wi-Fi network}
        %     \resumeItem{Structured codebase following MVVM architecture for clean codebase}
        %     \resumeItem{Utilized RxJava for asynchronous data retrieval to increase smooth user experience}
        %   \resumeItemListEnd
      \fi

    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {St. Edward's University}{Austin, Texas}
      {Bachelor of Science in Computer Science}{Aug. 2018 - Jun. 2023}
        \resumeItemListStart
          \resumeItem{Relevant Courseworks: Software Engineering, Mobile Programming, User Interface \& User Experience, Programming Languages, Web Programming}  
         \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
